\documentclass[11pt]{article}
\usepackage{graphicx}
\usepackage{placeins}
\usepackage{url}
\usepackage{cite}
\usepackage{geometry}
\geometry{top=2cm}

\input{crisdefs.tex}

\newcommand {\reply} {\mbox{\small REPLY}}

\begin{document}

\title{Author's Response to Reviewer \#1 }

\author{AIRS Deconvolution and the \\
       Translation of AIRS to CrIS Radiances \\ 
       with Applications for the IR Climate Record \\
       \\
       Howard~E.~Motteler, L.~Larrabee~Strow}

\maketitle

\section{General Remarks}

We thank the reviewers for their thoughtful comments and have tried
to incorporate or respond to all suggestions and questions.  In the
remainder of this section we summarize the main changes we've made.
Section~2 consists of reviewer's comments followed by our responses.

The discussion of reference truth for the deconvolution (starting on
page 3 line 30 RHS of the original submission) was not clear.  We
have updated the labels in figures 3 and 4 from ``gauss'' to ``decon
ref'' to better indicate we are showing the deconvolution reference
truth.  We updated the associated discussion to emphasize that the
deconvolution reference truth is intended as validation of the
deconvolution---we don't need it to do the deconvolution or for
subsequent reconvolution to CrIS or other targets.

We corrected the relationship of standard deviation and full-width
half-max (FWHM), $s=\fwhm / (2\sqrt{2\ln 2})$ in the original
submission, to $s=\fwhm / (2\sqrt{2}\,(\ln 2)^{1/(2p)})$.  The
latter is correct for the generalized Gaussian.  The difference is
small for the range of values $p$ we used.  As noted above this does
not effect the accuracy of the translations, just (to a very small
degree) reference truth for the deconvolution and the basis
functions for our L1d ``idealized grating model''.

The section on regression translation has been revised and
shortened.  We dropped the paragraph on adding noise since we don't
show those results.  The direct and principal component regression
matrices are now shown only for the MW, enough for an overview.  
The regression matrices are are now for apodized radiance, matching
the residuals.  The interpolation section in the appendix has been
revised to show apodized residuals and to emphasize the advantage of
using both the source and target response functions.

\section{Response to Comments}

\begin{itemize}

\item p.1 Line.14 r.h.s.: It would be useful to introduce here,
  rather than on p.3 and p.6, that the CrIS instrument has two modes
  of operation, the nominal and full spectral resolution (NSR and
  FSR, respectively).  It should also be mentioned that CrIS was in
  the NSR from launch in 10/28/2011 through Dec. 2014 or Dec. 2015
  (after bit-trim mask upgrade, depending how much detail you want
  to cover here.

  \reply: We agree this info should be given, but in section 3 (the
  AIRS to CrIS translation) rather than the introduction.  There is
  a limit to what fits in the introduction---for example we do not
  get into other significant details, such as AIRS L1b vs L1c,
  there.  The key idea of the paper is that we can get a modest
  resolution enhancement from the AIRS deconvolution and we do say
  that in the introduction.  As it turns out this is good enough for
  NSR but probably not FSR, but again the CrIS section is the
  natural place for that discussion.
  
% For this paper the CrIS and L1d translations are sample
% applications, not the main story.

\item p.1 Line.60 r.h.s.: ``The SRFs are not necessarily
  symmetrical, especially at the high end of the band.''  The SRFs
  are not necessarily symmetrical due to fringing in the AIRS
  entrance filters, especially at the high end of the band” is
  repetitive and can be combined into one sentence.

  \reply: Right, we fixed this.

\item p.1 Section 1: It might be best to simply include a table of
  significant instrument attributes for AIRS, IASI, and CrIS. Things
  like type (grating or interferometer), spectral sampling,
  resolution, launch dates, number of channels, and NEDN at selected
  frequencies.

  \reply: This would be interesting, but we can't really justify
  discussing IASI here in any detail, and AIRS and CrIS are
  different enough that the differences are not easily summed up in
  a table.  A short descriptive paragraph, expanding a bit on what
  we have now, is probably best.  The suggested table would find a
  better home in in a paper dealing with the many questions beyond
  response functions that come up in building a common data set.

\item p.2 Fig.1: It might be worth plotting this on a vertical log
  scale. The real AIRS SRF’s have a long tail that is not adequately
  demonstrated in a linear vertical scale. The “significant overlap”
  mentioned on p.~1 was by design as a Nyquist sampled spectrum was
  desired (as is IASI and CrIS) but there is additional significant
  overlap caused by the long-tail. These details should be briefly
  mentioned so the reader is not misled into thinking that AIRS can
  be represented by a simple Gaussian function in the equation that
  follows later on this page.

  \reply: It's interesting to look at the SRFs this way, and as you
  note the Gaussian approximation does not have the long tails of
  the tabulated SRFs.  We've added a comment to this effect.  But we
  aren't proposing to use the approximation as an alternative to the
  tabulated AIRS SRFS.  Our applications are reference truth for the
  deconvolved radiances (where they are used at a different spacing
  and higher resolving power than AIRS L1c), and as basis functions
  for the idealized grating model of section~4.

\item p.2 line 25 r.h.s.: on the first uses of the $||r||_2$ it
  would be helpful to let the reader know this is a Euclidian norm
  or even more obvious, a root sum square.

  \reply: We've added a note to that effect.  The notation used in
  the paper is taken from the Wikipedia articles for the
  Moore-Penrose inverse and mathematical norm, and we added both as
  citations.

\item p.2 line 37-39 r.h.s.: The $c$ in this equation is not the
  same as the $c$ used above (in $S_b r = c$). Suggest that a
  different symbol be used to avoid confusing the reader.

  \reply: Agreed, we replaced this with $s$.

\item p.3 line 45-50 r.h.s.: The CrIS NSR mode will ultimately
  become a historical oddity for S-NPP. It is irrelevant for JPSS-1
  to JPSS-4 (ultimately to be known as NOAA-21, 22, 23, 24 if they
  survive launch) as the NSR will no longer be processed. Thus, the
  authors need to justify why they would degrade the entire AIRS
  2002 to 2016 and S-NPP/NOAA-20+ record from 2016 to 2030’s instead
  of potentially finding an alternative higher resolution grid. For
  example, consider the loss of spectral information in the AIRS
  carbon monoxide spectral domain when going from AIRS SRFs to CrIS
  NSR – the CO band information is completely lost. Similar loss
  occurs in the 2390 cm-1 R-branch that affects lower tropospheric
  temperature information.

  \reply: We agree, medium to long term.  But in the meantime we
  have the significant overlap of AIRS and CrIS NSR data to work
  with.  The effective resolution of deconvolved AIRS does not take
  us quite to CrIS FSR for the MW and SW bands.  You can still do a
  translation but the residuals are relatively large in comparison
  with those shown in the paper.

  One solution might be to pick an intermediate resolution for CrIS,
  for example 0.6 \wn\ in the MW, that roughly corresponds to the
  AIRS resolving power, and we've added a note to that effect.  
  This is easy to do for both regular CrIS processing and our AIRS
  to CrIS translation.  In both cases we have an intermediate
  representation---sensor grid for CrIS and our deconvolution grid
  for AIRS---that can be resampled to any nominal resolution we
  like.  We've expanded the discussion of NSR and FSR at the end of
  the CrIS translation section and used this topic as a lead-in to
  the next section, translation to an idealized grating model.

\item p.3 Fig.4: I had a tough time understanding exactly what was
  plotted here and I think the text and caption could be improved.
  I believe AIRS is the original AIRS radiance. Kcarta is the 0.0025
  cm-1 LBL representation, the Gauss and decon are a comparison of
  the 0.1 cm-1 intermediate resolution where Gauss is derived from
  direct convolution of k-Carta and decon is derived by the
  pseudo-inverse process – but I am not sure if I have Gauss/Decon
  flipped. It would be best if the plot labels and text were
  identified explicitly.

  \reply: Agreed.  We've update the figure labels and associated
  discussion.  In figures 3 and 4 the old label ``gauss'' is now
  ``decon ref'' (reference truth for the deconvolution) and the old
  ``decon'' is now ``AIRS decon'' (deconvolved AIRS radiances).

\item p.4 line 34 l.h.s.: given that Hamming apodization is
  reversible there cannot be any loss in spectral resolution. Thus,
  the appearance of the radiances in unapodized (or deapodized since
  there is self- apodization effects with CrIS) versus Hamming
  apodized only has to do with non-local ILS effects (i.e.,
  side-lobes of the SRF) and not resolution. The 15 micron band line
  spacing is a resonance that is aliased with the CrIS OPD, such
  that the sinc() function produces a distortion of that band (i.e.,
  the peaks and troughs are exaggerated).

  \reply: We agree there is no loss in interferometric resolution
  with an invertible apodization.  Hamming apodization does reduce
  resolving power $R = v_i/ \fwhm_i$, since it increases $\fwhm$
  while decreasing the side-lobes.  We changed ``resolution'' to
  ``resolving power'' and set Barnet et al. 2000 as noted below as
  our first citation for apodization, for the sentence in question.

% For the deconvolution-based translation apodization is a separate,
% distinct step after deconvolution and reconvolution or resampling
% to the final user grid, 

% and our ``true Cris'' minus ``AIRS CrIS'' residuals are
% significantly smaller with apodization.  This is true for almost
% every sort of test we do, for example comparing calibrated
% measured and calculated radiances.
  
\item p.4 line.34 l.h.s.: The AIRS SRF is a modified Gaussian that
  is mostly a local function. It seems odd that the authors would
  propose convert AIRS to a unapodized SRF since the sinc() function
  is a lon-local function. That is, all AIRS channels would be
  necessary to produce a CrIS sinc() function. Alternatively, if one
  were to convert the AIRS channels to CrIS Hamming channels then
  each CrIS channel would be reconstructed from a small and local
  set of AIRS channels. The Hamming apodized radiances could then be
  converted to unapodized via a transformation as suggested in
  Barnet, C.D., J.M. Blaisdell and J.  Susskind 2000. Practical
  methods for rapid and accurate computation of interferometric
  spectra for remote sensing applications. IEEE
  Trans. Geosci. Remote Sens. v.38 p.169-183.

  \reply: The deconvolution-based translation is a two-step process:
  (1) deconvolution from AIRS L1c channels to a regularly spaced
  $0.1$~\wn\ grid spanning the AIRS channels, or an AIRS and CrIS
  band intersection, followed by (2) a conventional convolution 
  (via resampling or a zero-filled double Fourier transform) to the
  CrIS user grid, followed by optional Hamming or other apodization.
  So all AIRS channels are in fact available (in the sense of
  contributing to the $0.1$~\wn\ grid) to produce a CrIS sinc
  response function.

  The deconvolution is done by starting with is real measured AIRS
  SRFs tabulated at a $0.1~\wn$ grid.  This is our matrix $S_b$.  We
  invert this and apply it as a linear transform $r = S_b^{-1} c$ to
  get deconvolved radiances at the $0.1~\wn$ grid.  Both $S_b$ and 
  $S_b^{-1}$ are banded transforms, and this is the locality that
  matters for the deconvolution.  Figure 5a shows some sample rows of
  $S_b^{-1}$.

  For the regression of section 5, if we regress against unapodized
  radiances and then apply apodization we get results very close to
  regression against apodized radiances, and if we regress against
  apodized radiances and apply a deapodization, we get results very
  close to regression against unapodized radiances.  So for both
  regular and principal component regression it doesn't seem to
  matter if the target is apodized or unapodized CrIS radiances.

  We have found an apodized target as suggested in your citation is
  a powerful tool for doing fast transmittance radiative transfer
  models---it was much easer to do the coefficient fitting with
  apodized transmittances, and deapodize radiances as needed.
  
%  The Gaussian basis is used to convolve kcarta radiances in an
%  attempt to get a rough reference truth for the deconvolution; it
%  is not actually used for either the deconvolution or subsequent
%  reconvolution to CrIS radiances.

\item p.4 line 39-56 l.h.s.: this discussion adds confusion. It
  looks like the 49 set will be used for training and the 7377 is
  the independent set. Seems like this could be said most
  succinctly.

  \reply: Agreed, and we've rewritten this paragraph.  The 49
  profile set is always the test or independent set, as it makes for
  a more strict test.

\item p.4 line 54-59 r.h.s. Could the authors give some explanation
  as to the physical basis for the statistical correction they are
  about to discuss. I was completely lost as to why this should be
  necessary. One concern came to mind and I will share it here. It
  seems like this ``ringing'' or ``regularity'' could be caused by
  trying to compute a sinc() function from a regularly spaced
  intermediate Gaussian (that also has side-lobes). The fact that it
  is diminished by Hamming says it might be an artifact caused by
  the sinc() side-lobes or band edges. Maybe this is a naïve idea
  (or at least it might give you a clue how to improve this
  discussion), but why did you not consider 0.1 cm-1 boxcars for the
  intermediate spectrum that would have perfect localization?

  \reply: the motivation for the statistical correction was simply
  that the residuals showed some regular structure and the standard
  deviation was relativly small.  The deconvolution is an imperfect
  process, so it seemed plausible that a correction might help.

  The Gaussian basis was used to convolve kcarta radiances to get
  reference truth for the deconvolution; it is not actually used 
  for either the deconvolution or subsequent reconvolution to CrIS
  radiances.  We did try a number of other functions for this
  reference truth, including the 0.1 cm-1 boxcar you suggest.  As I
  recall 0.2 cm-1 gave slightly smaller residuals, but both were
  larger than for the generalized Gaussian.

  Figure 5 shows two adjacent rows of the deconvolution transform,
  $S_b^{-1}$.  This is applied to channel radiances $c$ to get
  deconvolved radiances $r = S_b^{-1} c$ at the 0.1 cm-1 grid.  
  Each deconvolution point is a linear combination of several AIRS
  channels.  So it seems at least plausible that a generalized
  Gaussian would work as a basis function for the deconvoltuion
  reference truth.

% We are undoing the AIRS convolution, but only imperfectly.

\item p.6 line 48-55 l.h.s.~and p.~8 line 52-55: For most
  applications the noise spectral correlation is something that
  needs to be specified.  Since you have used linear transformations
  you have potentially altered the amplitude of the random component
  of NEDN and potentially added significant correlation (see Barnet
  2000 reference for a discussion of this in the application of
  apodization). Any data assimilation or retrieval application would
  be strongly impacted by this correlation. Given that one
  application of this methodology is for climate data records, it is
  worth discussing if the NEDN can be accurately translated.  The
  AIRS, IASI, and CrIS have similar information content in the
  signal-to-noise; however, if only the signal (radiance spectra)
  are transformed and not the noise than this process could, in
  fact, alter the information content such that AIRS, IASI, and CrIS
  cannot be combined in a meaningful manner. This thought is tied to
  the comments given on p.3 line 45-50 r.h.s. above.

  \reply: We've expanded the subsection on NEdN with the following
  comments.  The AIRS instrument does have some noise correlation,
  mainly within modules.  The question of correlation becomes more
  complex with the translation to L1c.  In contrast CrIS instrument
  noise is largely uncorrelated.

  In the paper we give reasonable estimates of NEdN for the AIRS to
  CrIS translation, assuming normally distributed AIRS noise.  These
  estimates (which are measured noise of the translation) do take
  into account correlations arising from the translation.  The
  translation to apodized CrIS reduces NEdN significantly for all 3
  bands.  Translation to unapodized CrIS also reduces NEdN for the
  MW and SW bands.  For the LW NEdN is similar up to about 900 cm-1
  and then a little higher past that.

  The effect of the deconvolution-based translation is similar to a
  mild apodization, and so should have a generally similar effect on
  the correlated component of AIRS noise.  Since we are reducing
  NEdN in the translation (except for the LW unapodized case), it
  seems unlikely we are increasing problems with the correlated
  component, except perhaps relative to the reduced NEdN.  But to
  prove that we'd need a plausible model of L1c noise correlation,
  which we do not have at the present time.

%   So the problem of correlation in the translation is likely no
%   worse that the problem of correlation in the original data.

%   \reply: The AIRS instrument does have some noise correlation,
%   mainly within modules.  The question of correlation becomes more
%   complex with the translation to L1c.  In contrast CrIS instrument
%   noise is largely uncorrelated.
% 
%   The translation adds noise correlation to exactly the extent 
%   that it adds signal correlation.  This is characterized by the
%   transform matrix.  Sample rows are shown in figure 5b for the L1c
%   to L1d (idealized grating) transform, and sample matrices in the
%   regression section.  We don't have an explicit transform matrix
%   for the AIRS to CrIS translation but did check cross correlation
%   for translated data, staring from normally distributed simulated
%   AIRS noise at the AIRS NEdN spec.  The measured correlation matrix
%   looks like a slightly fuzzy version of a transform matrix.
% 
%   The overall effect for the deconvolution-based translations is 
%   a slight spreading (across channels) of any correlation in the
%   original data.  This would be a problem for the translated data at
%   least to the extent it is a problem for the original AIRS data.
%   We have proposed adding noise to either AIRS or CrIS as needed for
%   a common product, and it should be possible to add correlations to
%   the CrIS noise to roughly match the AIRS.  But that's a matter for
%   future work.

\item p.6 line 47-48 r.h.s.: see comment for p.3 line 45-50 r.h.s. –
  this seems worthy of a bit more discussion given that this
  approach has been advertised as a solution for a climate data
  record.

  \reply: Agreed, we've expanded this, as discussed earlier.

\item p.10 line 38-58 l.h.s. (and p.4 line 47-49 r.h.s): this is a
  trivial point. The conventional interpolation would be the wrong
  thing to do. For interferometers an exact transformation could be
  done via cosine transforms (presumably what you are doing for the
  IASI-to-CrIS transformations). The issue here is what is the best
  manner to transform a grating instrument with non-ideal SRF’s to
  an interferometer system. Maybe this discussion is leading towards
  an alternate solution – converting all instruments to an idealized
  SRF which preserves the signal-to-noise as best as possible. This
  would be an ideal localized function that is Nyquist sampled and
  has minimum noise correlation (similar to the discussion on p.7
  l.h.s., but with the noise component discussed also). The AIRS is
  nearly a localized, Nyquist sampled, spectrum whereas the CrIS and
  IASI unapodized (or more properly deapodized) spectrum is
  not-ideal and introduces significant spectral distortion. The CrIS
  and IASI apodized spectra is nearly localized by the Hamming
  function has significant (1\%) side-lobes that diminish somewhat
  slowly (see Barnet 2000 for discussion).

  \reply: Some non-trivial algorithms do start from conventional
  interpolation of AIRS data.  For example the JPL algorithm for
  small frequency shifts uses a cubic spline augmented with a
  statistical fit for the derivatives near the initial channel
  frequencies.  This works better than deconvolution followed by
  reconvolution to a shifted grid, but only for the very small
  shifts characteristic of AIRS frequency drift.

  The main point of the interpolation section is the significance 
  of taking both source and target response function into account.
  Residuals for spline interpolation alone are shown to be larger
  that for spline interpolation to an intermediate grid followed by
  convolution to the CrIS user grid, and residuals for both are
  significantly larger than for AIRS deconvolution followed by the
  CrIS convolution.  Before switching to the deconvolution based
  translation we sometimes did use spline interpolation to a regular
  intermediate grid before reconvolution to the CrIS, thought this
  was never really satisfactory.  Our take on the relevance of all
  this was to demote the interpolation section to an appendix.
  
  The ``L1d basis'' is our version of the idealized SRF you suggest.
  It started out as an attempt at finding an approximate, relatively
  simple model for the AIRS SRFs.  We agree this is an interesting
  alternative to some kind of intermediate CrIS resolution as the
  target for a common data set.  A key point of the paper that the
  AIRS deconvolution is useful for more than one final target; from
  that point of view the intermediate CrIS resolution and L1d basis
  are sample applications.

\end{itemize}
\end{document}

